### 2019-02-05 thesis_report/conclusion.tex
Added structure

% -*- root: ./report.tex -*-
\chapter{Conclusion}
In the model we study, the introduction of a zigzag geometry increases the topological gap by several orders of magnitude while simultaneously reducing the Majorana length.
Additionally, the breaking of a chiral symmetry brings the system from the BDI symmetry class into the D symmetry class, resulting in a cleaner topological phase.  % Bas: how is the symmetry broken?
Together, these improvements directly affect the robustness of the Majorana state, potentially bringing us closer to reliably create topological devices.

>>>>

% -*- root: ./report.tex -*-
\chapter{Conclusion}\label{chap:conclusion}
In the model we study, the introduction of a zigzag geometry increases the topological gap by several orders of magnitude while simultaneously reducing the Majorana length.
Additionally, the breaking of a chiral symmetry brings the system from the BDI symmetry class into the D symmetry class, resulting in a cleaner topological phase.  % Bas: how is the symmetry broken?
Together, these improvements directly affect the robustness of the Majorana state, potentially bringing us closer to reliably create topological devices.

### 2019-02-05 thesis_report/introduction.tex
Added structure

	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as the reduction of the Majorana coherence length.
	Furthermore, we hypothesize that the gap improvement is the result of the elimination of long trajectories

>>>>

	In this thesis we show that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as the reduction of the Majorana coherence length.
	Furthermore, we hypothesize that the gap improvement is the result of the elimination of long trajectories.
	In order to verify this claim, we propose a simplified model of the zigzag system such that we can isolate the dependence of the gap on the length of available trajectories.

	In Chapter \ref{chap:theory}, we give an overview of established theory relevant to the understanding of this thesis.
	Subsequently, in Chapter \ref{chap:methods} we discuss the various methods used for the analysis of zigzag systems, of which the results are discussed in chapter \ref{chap:results}.
	Finally, in Chapter \ref{chap:conclusion}, we discuss the findings of this thesis, as well as an outlook on further research to be performed.
